Time Series Bootstrapping For Solar Current

### 2021-12-08 deliverables/presentation.Rmd
Added code for generating bootstrap histogram, and histogram in presentation
Reordered first slides

@@

- Understanding renewable energy sources like solar power is critical to the next century.
- PV modules installed at individual households/nodes reduce the overall load on the electrical grid.
- Balancing the expected contribution of an individual PV module with the expected residual demand required of the grid is a large optimization problem.
    - We dealt with half of that optimization problem

@@

>>>>

- Renewable energy solutions
- Problem: balance contribution of PV modules with demand on electrical grid
  - Our work deals with the expected PV contribution

@@

@@

![](./images/mean_boot_plot.png)
